Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-01-31 paper/main.tex
plot for different budgets
remove previous plot

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,bm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{bm}             % bold fonts for math symbols
\usepackage[misc]{ifsym}    % collection of symbols
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}          % force figure positioning in text
\usepackage{chngcntr}       % counters per section
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{dateplot, groupplots}
\pgfplotsset{compat=newest}
\usepackage{plotpolicies}   % custom package to plot policy-executions

@@

@@

\begin{figure}
    \centering
    \begin{tikzpicture}
        \pgfplotsset{
          scale only axis,
          height=6cm,
          xlabel={Cumulative number of daily new hospitalizations},
          ylabel={Cumulative lost contacts}
        }
      \begin{axis}[
        legend entries={{$\text{PCN}_\text{ARH}$ (ODE)}, {$\text{PCN}_\text{ARI}$ (ODE)}, {Fixed}},
        width=9.5cm
      ]
      %\addplot[only marks,draw opacity=0.5,mark=x,green] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_ode.csv};
      \addplot[only marks,draw opacity=0.5,mark=x,red] table [x=o_1, y=o_5, col sep=comma] {data/cs/arh/cs_ode.csv};
      \addplot[only marks,draw opacity=0.5,mark=o,blue] table [x=o_1, y=o_5, col sep=comma] {data/cs/ari/cs_ode.csv};
      %\addplot[only marks,mark=o,yellow] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_binomial.csv};
      %\addplot[only marks,draw opacity=0.5,mark=o,blue] table [x=o_1, y=o_5, col sep=comma] {data/cs/arh/cs_binomial.csv};
      %\addplot[only marks,draw opacity=0.5,mark=diamond,cyan] table [x=o_1, y=o_5, col sep=comma] {data/cs/ari/cs_binomial.csv};
      \addplot[only marks,mark=+] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_fixed.csv};
      \end{axis}
    \end{tikzpicture}
    \caption{The Pareto front of policies discovered by PCN using the ODE model (Binomial omitted for clarity, see SI), showing the different compromises between the number of hospitalizations and the number of lost contacts. Although $\text{PCN}_\text{ARI}$ was trained on the number of infections, it still shows a competitive coverage set with respect to hospitalizations.}
    \label{fig:pareto-front}
\end{figure}

@@

\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}
\counterwithin{equation}{section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
RL has also been used to learn effective mitigation strategies which limit the spread of COVID-19 \cite{ohi2020exploring}. Kwak et al. \cite{kwak2021covid} use deep RL, with an SIRD model, to learn efficacy of lockdown and travel restrictions in controlling the COVID-19 pandemic using data collected from various government organisations.  Bastani et al. \cite{bastani2021efficient} use a RL algorithm called Eva to limit the influx of asymptomatic travellers infected with SARS-CoV-2 to Greece. Kompella et al. \cite{kompella2020reinforcement} define a COVID-19 simulator and a methodology to learn mitigation policies that minimize the economic impact without overwhelming the hospital capacity. RL has also been used to learn effective COVID-19 vaccination distribution strategies \cite{beigi2021application,awasthi2020vacsim} and to create decision support systems for mitigating the spread of COVID-19.

\end{document}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,bm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{bm}             % bold fonts for math symbols
\usepackage[misc]{ifsym}    % collection of symbols
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}          % force figure positioning in text
\usepackage{chngcntr}       % counters per section
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{comment}
\usepgfplotslibrary{dateplot, groupplots}
\pgfplotsset{compat=newest}
\usepackage{plotpolicies}   % custom package to plot policy-executions

@@

% color scheme for plots: plot-color-i
\definecolor{pc1}{RGB}{76, 120, 168}
\definecolor{pc2}{RGB}{245, 133, 24}
\definecolor{pc3}{RGB}{228, 87, 88}
\definecolor{pc4}{RGB}{114, 183, 178}
\definecolor{pc5}{RGB}{84, 162, 75}
\definecolor{pc6}{RGB}{238, 202, 59}
\definecolor{pc7}{RGB}{178, 121, 162}

@@

\begin{figure}
    \centering
    \input{fig/arh.tex}
    \caption{The Pareto front of policies discovered by PCN using the ODE model (Binomial omitted for clarity, see SI), showing the different compromises between the number of hospitalizations and the number of lost contacts. Although $\text{PCN}_\text{ARI}$ was trained on the number of infections, it still shows a competitive coverage set with respect to hospitalizations.}
    \label{fig:pareto-front}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}
\counterwithin{equation}{section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
RL has also been used to learn effective mitigation strategies which limit the spread of COVID-19 \cite{ohi2020exploring}. Kwak et al. \cite{kwak2021covid} use deep RL, with an SIRD model, to learn efficacy of lockdown and travel restrictions in controlling the COVID-19 pandemic using data collected from various government organisations.  Bastani et al. \cite{bastani2021efficient} use a RL algorithm called Eva to limit the influx of asymptomatic travellers infected with SARS-CoV-2 to Greece. Kompella et al. \cite{kompella2020reinforcement} define a COVID-19 simulator and a methodology to learn mitigation policies that minimize the economic impact without overwhelming the hospital capacity. RL has also been used to learn effective COVID-19 vaccination distribution strategies \cite{beigi2021application,awasthi2020vacsim} and to create decision support systems for mitigating the spread of COVID-19.
\end{comment}
\end{document}
